### 2020-07-10 Thesis-Chapter1-Introduction.tex
Address several more todos; add some reading sources

The conflict at the heart of the encryption and \ac{EA} debate is that the same cryptographic and design principles that
underlie nearly all digital security also enable an unprecedented degree of individual privacy. Encryption is a
foundational tool to the integrity and confidentiality of all connected computing systems. Its increasing ubiquity in
communications and storage provides clear benefits and should be welcomed by all. In a world where information security
is frightfully poor yet increasingly important, strong encryption's necessity can not be understated. However, the
privacy afforded by certain encryption technologies hampers law enforcement investigations and hides wrongdoing. 
% TODO: citation
In a
society that cares about bringing wrongdoers to justice, this risk should not be ignored.

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties. 
% TODO: citation
Human rights groups and technical leaders counter that a weakened
encryption environment would fatally compromise privacy and security as we know it. 
% TODO: citation
As the debate continues, sides have
become entrenched, and both sides have engaged in disingenuous attacks against their perceived opponents.

@@

% TODO: use first person voice? Originally had wording like "this thesis introduces", but Kalafut says not to be afraid
% of "I". Could also use passive voice.

>>>>

The conflict at the heart of the encryption and \ac{EA} debate is that the same cryptographic and design principles that
underlie nearly all digital security also enable an unprecedented degree of individual privacy. Encryption is a
foundational tool to the integrity and confidentiality of all connected computing systems. Its increasing ubiquity in
communications and storage provides clear benefits and should be welcomed by all. In a world where information security
is frightfully poor yet increasingly important, strong encryption's necessity can not be understated. However, the
privacy afforded by certain encryption technologies hampers law enforcement investigations and hides wrongdoing
\cite{cox_2020} \cite{keller_internet_2019}. In a society that cares about bringing wrongdoers to justice, this risk
should not be ignored.

The conversation over encryption is in a stalemate. Governments and law enforcement agencies frequently cite the need to
access encrypted data to perform their duties \cite{ministerial_2018} \cite{fbi_2020}. Human rights groups and technical
leaders counter that a weakened encryption environment would fatally compromise privacy and security as we know it
\cite{ruiz_there_2018} \cite{abelson_2015}. As the debate continues, sides have become entrenched, and both sides have
engaged in disingenuous attacks against their opponents.

@@

### 2020-07-10 Thesis-Chapter2-Background.tex
Address several more todos; add some reading sources

% TODO: clarify relationship between encryption and cryptography?

@@

% TODO: add reference to future, comprehensive Appendix of all proposed encryption laws

@@

The \ac{SAFEAct} would have broadly protected ``use any encryption regardless of the encryption algorithm selected,
encryption key length chosen, or implementation technique or medium used,'' excepting ``the unlawful use of encryption
in furtherance of a criminal act.'' It also would have lifted export controls. The bill grew support as it was
reintroduced in consecutive congresses, but was abandoned when the Clinton administration adopted the act's
pro-encryption policies in 1999 \cite{kehl_right_2015}.

@@

\Ac{CESA} was a legislative proposal by Clinton administration introduced on same day as encryption policy changes that
led to the abandonment of the \ac{SAFEAct}. Section 102 lays out the government position precisely---encryption is an
important tool for information security, but is also used to ``hide unlawful activity by terrorists, drug traffickers,
child pornographers, and other criminals'' (the \ac{horsemen}), and therefore ``[a]ppropriate means must be available to
fulfill these law enforcement objectives.'' The bill would establish voluntary-participation third-party key escrow with
``recovery agents'' that would provide law enforcement with access to \ac{plaintext}. Access would be compelled through
a variety of mechanisms, including warrantless mechanisms through \ac{FISA}. The White House failed to attract a
member of Congress to officially sponsor the bill.

@@

Though this bill was not officially proposed, it represents one of the first legislative attempts to regulate encryption
in \ac{the-cw2}. This draft was released shortly after the close of the Apple vs. FBI case, and would have compelled
Apple to unlock the phone. Though it would not mandate a technical mechanism, the bill would have mandated that
manufacturers and service providers be able to provide \ac{EA}. This mandate notably goes beyond several regulatory
proposals in \ac{the-cw1}.
% TODO: how so?
Previewing a common phrase in recent \ac{EA} arguments \cite{geller_2019}, the draft's
authors both used the phrase ``above the law'' in promotion of the bill.
% TODO: how does this differ from the new LEAD Act?

@@

% TODO: as of 4/18/20, this bill is still active. Follow up.

@@

% \law{2019}{Technology in Criminal Justice Act}{demings_hr5227_2019}{
% % pfefferkorn_2019
% % And in fact, there’s already proposed legislation based on CSIS’s recommendations: the Technology in Criminal Justice
% % Act of 2019, introduced in the House last month by a bipartisan group of co-sponsors led by Rep. Val Demings of Florida.
% % The bill seeks to close the resource, training, and information-sharing gap for digital evidence, and to improve the
% % frayed relationship between law enforcement and technology companies. Notably absent from the bill is any language that
% % would roll back the CALEA compromise or mandate encryption backdoors. To be clear, I’m not advocating for or against
% % Rep. Demings’ bill. I just want to point out that it offers an alternative to whatever backdoor nightmare the Senate
% % Judiciary Committee is surely drafting up right now.
% }

@@

% TODO: as of 4/18/20, this bill is still active. Follow up.

@@

% IDEA: put this in an appendix too? Or its own chapter? Too much detail for the background section.
%
% Looking at it now, even what I have seems like too much. Maybe move it all to an appendix.
%
% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis)
%
% Since the enactment of the Regulation of Investigatory Powers Act 2000, the U.K. government had the ability to serve
% written notices requiring mandated decryption. Law enforcement and intelligence agencies also have explicit permission
% to perform ``computer network exploitation,'' and approach this thesis refers to as ``\ac{lawful-hacking}.'' 2016's
% Investigatory Powers Act expanded these capabilities and, among other additions, in section 253 created ``technical
% capability notices'' that the Secretary of State can issue to telecommunications operators mandating \ac{EA}
% \cite{legislature_2016}.

@@

    \country{European Countries}{acosta_government_2016}{
% France, Belgium, Germany, Sweden, EU
% EU GDPR \cite{parliament_2016}

% TODO: it is very important to know who these requirements apply to. Traditional telecoms, obviously. Facebook and
% Google? Signal and WhatsApp?

@@

% TODO: China, see also blanchard_2017

% TODO: but you can still get iPhones in China, right... ? Again, scope?

@@

% There are several types of approaches:
% TODO: my selections here are also rather sparse. Create another appendix? (I love work). Possibly create table of
% properties below, similar to denning_taxonomy_1996. savage_lawful_2018 has some good citations to mine.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
%   - See denning_taxonomy_1996
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

@@

% TODO: need an aside on shamir m/n secret sharing? Probably in order to understand split key approaches at all

@@

% TODO: reference forward chapter
Argdown is used in this thesis to analyze the arguments used in the \ac{EA} debate. \myfig{fig-args-demo} shows the
basic structure of arguments. Statements are positions on issues. Some statements are based on values that cannot be
addressed through argument. Statements and arguments may support or attack one another, and arguments support or
undercut other arguments.

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is
the primary concern. \myfig{fig-dfd-demo} shows the basic elements of a \ac{DFD}. In this thesis I create \acp{DFD} in
this style to analyze the threats already present and those that \ac{EA} would introduce.
% TODO: reference forward chapter

>>>>

% TODO: clarify relationship between encryption and cryptography. Use appropriately throughout.

@@

@@

The \ac{SAFEAct} would have broadly protected ``use any encryption regardless of the encryption algorithm selected,
encryption key length chosen, or implementation technique or medium used,'' excepting ``the unlawful use of encryption
in furtherance of a criminal act.'' It also would have lifted export controls. The bill grew support as it was
reintroduced in consecutive congresses, but was abandoned when the Clinton administration adopted the act's
pro-encryption policies in 1999 \cite{:kehl_right_2015}.

@@

\Ac{CESA} was a legislative proposal by Clinton administration introduced on same day as encryption policy changes that
led to the abandonment of the \ac{SAFEAct}. Section 102 lays out the government position precisely---encryption is an
important tool for information security, but is also used to ``hide unlawful activity by terrorists, drug traffickers,
child pornographers, and other criminals'' (the \ac{horsemen}), and therefore ``appropriate means must be available to
fulfill these law enforcement objectives.'' The bill would establish voluntary-participation third-party key escrow with
``recovery agents'' that would provide law enforcement with access to \ac{plaintext}. Access would be compelled through
a variety of mechanisms, including warrantless mechanisms through \ac{FISA}. The White House failed to attract a
member of Congress to officially sponsor the bill.

@@

Though this bill was not officially proposed, it represents one of the first legislative attempts to regulate encryption
in \ac{the-cw2}. This draft was released shortly after the close of the Apple vs. FBI case, and would have compelled
Apple to unlock the phone. Though it would not mandate a technical mechanism, the bill would have mandated that
manufacturers and service providers be able to provide \ac{EA}. This mandate notably goes beyond several regulatory
proposals in \ac{the-cw1} by forcing platform and application developers to comply. Previewing a common phrase in recent
\ac{EA} arguments \cite{geller_2019}, the draft's authors both used the phrase ``above the law'' in promotion of the
bill.

@@

% TODO: as of 7/10/20, this bill is still active. Follow up.

@@

@@

% TODO: Update based on new amendment.

@@

% IDEA: put this in an appendix too? Or its own chapter? Too much detail for the background section.
%
% For more, read donahue_comparative_2018 (Israel and China) and budish_encryption_2018 (framework for analysis)
%
% Since the enactment of the Regulation of Investigatory Powers Act 2000, the U.K. government had the ability to serve
% written notices requiring mandated decryption. Law enforcement and intelligence agencies also have explicit permission
% to perform ``computer network exploitation,'' and approach this thesis refers to as ``\ac{lawful-hacking}.'' 2016's
% Investigatory Powers Act expanded these capabilities and, among other additions, in section 253 created ``technical
% capability notices'' that the Secretary of State can issue to telecommunications operators mandating \ac{EA}
% \cite{legislature_2016}.

@@

    \country{European Countries}{acosta_government_2016}{

% TODO: it is very important to know who these requirements apply to. Traditional telecoms, obviously. Facebook and
% Google? Signal and WhatsApp? Telecoms, not platforms or apps. This is the big differentiator. This can be expanded
% upon when I talk a bit about pen registers, etc.

@@

@@

% There are several types of approaches:
% IDEA: my selections here are also rather sparse. Create another appendix? (I love work). Possibly create table of
% properties below, similar to denning_taxonomy_1996. savage_lawful_2018 has some good citations to mine.
% - Allow strong encryption (anyone with the users' private keys can see it)
% - Disallow encryption (anyone can see it)
% - Make encryption sufficiently weak, e.g. limit key length (anyone with enough CPU can see it)
% - Require use of backdoored algorithms, security via obscurity (anyone with the secret knowledge can see it)
% - Allow any encryption, just be able to provide keys (anyone with the extra keys can see it)
%   - Store extra in gov't DBs, in corporate DBs, in third-party DBs, on blockchain, in secure HW on device
%   - Split the key and store it multiple places
%   - See denning_taxonomy_1996
% - Use some alternative path
%   - Coerced passwords, finding unencrypted copies, seizing devices while unlocked, lawful hacking

@@

@@

Argdown is used in \mychap{chap-arguments} to analyze the arguments used in the \ac{EA} debate. \myfig{fig-args-demo}
shows the basic structure of arguments. Statements are positions on issues. Some statements are based on values that
cannot be addressed through argument. Statements and arguments may support or attack one another, and arguments support
or undercut other arguments.

@@

\Acp{DFD} are one tool designed to address these questions. \Acp{DFD} feature processes, data flows, data stores, and
external entities. \Acp{DFD} are well suited for threat modeling because security vulnerabilities tend to follow data
flow, not control flow \cite{shostack_threat_2014}. They are particularly well suited for \ac{EA}, as data privacy is
the primary concern. \myfig{fig-dfd-demo} shows the basic elements of a \ac{DFD}. In \mychap{chap-threatmodel} I create
\acp{DFD} in this style to analyze the threats already present and those that \ac{EA} would introduce.
